A meta-analysis of powdery mildew yield loss mitigation strategies in Australian mungbean

### 2020-06-24 03_Prep_data.Rmd
revert

```{r variance_types}
PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole") %>%
   group_by(trial_ref, location, year , Y_error_type, fungicide_ai) %>%
   summarise(DMI_treatments = length(Y_error_type)) %>%
   arrange(Y_error_type) %>%
   select(!fungicide_ai) %>%
   kable(caption = "Number of treatments for each trial and the error type reported", align = "c") %>%
   footnote(general = "DMI - demethylation inhibitors (tebuconazole and propiconazole).")
```

>>>>

```{r variance_types}
PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole"|
             fungicide_ai == "200 g/L azoxystrobin + 80 g/L cyproconazole") %>%
   group_by(trial_ref, location, year , Y_error_type, fungicide_ai) %>%
   summarise(DMI_treatments = length(Y_error_type)) %>%
   arrange(Y_error_type) %>%
   select(!fungicide_ai) %>%
   kable(caption = "Number of treatments for each trial and the error type reported", align = "c") %>%
   footnote(general = "DMI - demethylation inhibitors (tebuconazole and propiconazole).")
```
